### 2009-05-25 doc/manuals/janitor/tex_usage/usage.tex
Series of updates to the Janitor documentation.
Some typos fixed.

Janitor can be used either with or without A-REX. In case A-REX is used, installations will be maintained automatically the runtime environments.

@@

Runtime Environments can be specified using the supported job description languages.
Representative two common languages shall be explained at this point: xRSL and JSDL.
Listing~\ref{lst:xrsl_job} shows the xRSL example in which two runtime environments are requested.

@@

In addition of using Janitor together with A-REX, Janitor can also be used as a standalone commandline tool.
The available commands are listed in the Table~\ref{janitor_commandline_man}.
\begin{table}[!h]
   \begin{center}
        \mycaption{Overview about the available commands in Janitor.}{}
        \label{tab:janitor_commandline_man}
	\begin{tabular}{p{0.5cm}p{2cm}p{11cm}}
	\multicolumn{3}{l}{\textbf{janitor [COMMAND] [JOB-ID] [RTE] \dots}} \\
	\multicolumn{3}{l}{\textbf{Command:}}\\
	&	register			& Registers a job and a set of runtime environments in the Janitor database. Requires the parameters [JOB-ID] and a list of [RTE]s.\\
	&	deploy				& Downloads and installs the desired runtime environments. Requires the name of an already registered [JOB-ID].\\
	&	remove				& Removes the placeholder of the job on the runtime environments. If no more jobs are using the runtime environment and the lifespan of the runtime environment has be expired, the runtime environment can be removed using the \texttt{sweep} command. Requires the [JOB-ID] to be removed.\\
	&					&\\
	&	sweep				& Removes unused runtime environments. No further arguements are required. Using the option \texttt{--force} enforces the removal of all unused runtime environments. Runtime environments having the state FAILED will not be removed.\\
	&	setstate			& Changes the state of a dynamically installed runtime environment. This might be useful in case a runtime environment with a state FAILED shall be removed (new state might be REMOVAL\_PENDING). Requires the argument [STATE] followd by a list of [RTE]s.\\
	&					&\\
	&	search				& Performs a simple search in the catalog and the manually installed runtime environments (\texttt{runtimedir}). Requires no [JOB-ID] nor [RTE]s, but only a list of string to be searched for.\\
	&	list				& Lists all information about jobs, automatically installed runtime environments and manually installed runtime environments. No additional parameters have to be passed.\\
	&	info				& Renders information about a job. Requires the parameter [JOB-ID].\\
	\multicolumn{3}{l}{\textbf{Job id:}}\\
	&					& A unique sequence of numbers. Once Janitor registered a job id it cannot register a second job having the same job id.\\
	\multicolumn{3}{l}{\textbf{Runtime environments:}}\\
	&					& Runtime environments are defined by a continuous string. The name of valid runtime environment names can be investigated using the \texttt{list} or the \texttt{search} commands. They are defined in the catalog or by the directories and scripts of the \texttt{runtimedir} of the \texttt{grid-manager}.\\
	\end{tabular} 
   \end{center}
\end{table}
The most important commands for Janitor are \texttt{register}, \texttt{deploy} and \texttt{remove}. In order to 
register a job along with a set of runtime environments in Janitor, the first command \texttt{register} followed
by a job identifier and a list of runtime environments has to be used.
A job is identified by sequence of numbers. Runtime environments are specified by a string containing the name as it is defined 
within the catalog (resp. the runtime directory of the grid-manager).
The command \texttt{deploy} extracts the necessary dependcies of the desired runtime environments and then downloads and installs 
the required packages. %How dependecies can are defined will be explained later in the section~\ref{sec:catalog}.

@@

Each command has a certain behaviour for its exit status. The Table~\ref{tab:janitor_commandline_exit_status} lists the possible
outcomes.

>>>>

The Janitor can be used either with or without A-REX. In case A-REX is used, installations will be maintained automatically the runtime environments.

@@

Runtime Environments can be specified using the supported job description languages.
The most representative two common languages shall be explained at this point: xRSL and JSDL.
Listing~\ref{lst:xrsl_job} shows the xRSL example in which two runtime environments are requested.

@@

In addition to using the Janitor together with A-REX, the Janitor can also be used as a standalone commandline tool.
The available commands are listed in the Table~\ref{janitor_commandline_man}.
\begin{table}[!h]
   \begin{center}
        \mycaption{Overview about the available commands in Janitor.}{}
        \label{tab:janitor_commandline_man}
	\begin{tabular}{p{0.5cm}p{2cm}p{11cm}}
	\multicolumn{3}{l}{\textbf{janitor [COMMAND] [JOB-ID] [RTE] \dots}} \\
	\multicolumn{3}{l}{\textbf{Command:}}\\
	&	register			& Registers a job and a set of runtime environments in the Janitor database. Requires the parameters [JOB-ID] and a list of [RTE]s.\\
	&	deploy				& Downloads and installs the desired runtime environments. Requires the name of an already registered [JOB-ID].\\
	&	remove				& Removes the placeholder of the job on the runtime environments. If no more jobs are using the runtime environment and the lifespan of the runtime environment has be expired, the runtime environment can be removed using the \texttt{sweep} command. Requires the [JOB-ID] to be removed.\\
	&					&\\
	&	sweep				& Removes unused runtime environments. No further arguements are required. Using the option \texttt{--force} enforces the removal of all unused runtime environments. Runtime environments having the state FAILED will not be removed.\\
	&	setstate			& Changes the state of a dynamically installed runtime environment. This might be useful in case a runtime environment with a state FAILED shall be removed (new state might be REMOVAL\_PENDING). Requires the argument [STATE] followd by a list of [RTE]s.\\
	&					&\\
	&	search				& Performs a simple search in the catalog and the manually installed runtime environments (\texttt{runtimedir}). Requires no [JOB-ID] nor [RTE]s, but only a list of string to be searched for.\\
	&	list				& Lists all information about jobs, automatically installed runtime environments and manually installed runtime environments. No additional parameters have to be passed.\\
	&	info				& Renders information about a job. Requires the parameter [JOB-ID].\\
	\multicolumn{3}{l}{\textbf{Job id:}}\\
	&					& A unique sequence of numbers. Once Janitor registered a job id it cannot register a second job having the same job id.\\
	\multicolumn{3}{l}{\textbf{Runtime environments:}}\\
	&					& Runtime environments are defined by a continuous string. The name of valid runtime environment names can be investigated using the \texttt{list} or the \texttt{search} commands. They are defined in the catalog or by the directories and scripts of the \texttt{runtimedir} of the \texttt{grid-manager}.\\
	\end{tabular} 
   \end{center}
\end{table}
The most important commands for the Janitor are \texttt{register}, \texttt{deploy} and \texttt{remove}. To 
register a job along with a set of runtime environments in Janitor, the first command \texttt{register} followed
by a job identifier and a list of runtime environments has to be used.
A job is identified by a sequence of numbers. Runtime environments are specified by a string containing the name as it is defined 
within the Catalog (resp. the runtime directory of the grid-manager).
The command \texttt{deploy} extracts the necessary dependencies of the desired runtime environments to then download and install
the required packages. %How dependecies can are defined will be explained later in the section~\ref{sec:catalog}.

@@

Every command has a certain behaviour for its exit status. The Table~\ref{tab:janitor_commandline_exit_status} lists the possible
outcomes.
